### UI Trust Fund, Funding, and Payment Visualization

## Three data sets: "TWBState", "TWBYear", and "TFYear." "State" is IV state. 
## (This is the more frequently used of the set.) "Year" is IV year.

## X (Independent Variables) - Taxable Wage Base (TWB), Trust Fund (TF), Maximum
## Weekly Benefit Amount (MWBA).
## Y (Dependent variables) - Political party affiliation (Republican 
## Governor(RG) v Democratic Governor (DG), Republican President (RP) v 
## Democratic President (DP), Population, Geographic Area, and 
## Gross Domestic Product (GDP).

## Hypothesis 1: States with higher trust fund amounts will have higher taxable 
## wage base.
## H2: States with lower MWBA will have lower TWB, higher TFs.
## H3: In states that see a change from Republican to Democratic administrations,
## there will be higher TWBs, lower TFs, higher MWBAs.

library(readxl)
TWBState <- read_excel("C:/Users/Bridgette/Desktop/UI Tax Project/TWBState.xlsx", 
    guess_max = min(2000, n_max = NULL))
library(readxl)
TWBYear <- read_excel("C:/Users/Bridgette/Desktop/UI Tax Project/TWBYear.xlsx", 
    guess_max = min(2000, n_max = NULL))
library(readxl)
TFYear <- read_excel("C:/Users/Bridgette/Desktop//UI Tax Project/TFYear.xlsx", 
    guess_max = min(2000, n_max = NULL))
    
### NEED TO TAKE ADJUSTED TF AND APPLY IT ACROSS THE BOARD TO OTHER VIZ.

### Basic TWB by TF.
## Scatterplot of Taxable Wage Base by Trust Fund in Previous Year.
```{r}
TFP21 <- lm(TWB21 ~ TF20, data = TWBState)
summary(TFP21)

p1 <- ggplot(TWBState, aes(y=TF20, x=TWB21)) +
  geom_smooth(method=lm, se=FALSE) +
  xlab("Taxable Wage Base 2021 by State") +
  ylab("Trust Fund 2020 by State") +
  geom_text(label = TWBState$State, size = 2) +
  coord_cartesian(ylim = c(0, 5000))
p2 <- ggplot(TWBState, aes(y=TF19, x=TWB20)) +
  geom_smooth(method=lm, se=FALSE) +
  xlab("Taxable Wage Base 2020 by State") +
  ylab("Trust Fund 2019 by State") +
  geom_text(label = TWBState$State, size = 2) +
  coord_cartesian(ylim = c(0, 5000))
p3 <- ggplot(TWBState, aes(y=TF18, x=TWB19)) +
  geom_smooth(method=lm, se=FALSE) +
  xlab("Taxable Wage Base 2019 by State") +
  ylab("Trust Fund 2018 by State") +
  geom_text(label = TWBState$State, size = 2) +
  coord_cartesian(ylim = c(0, 5000))
p4 <- ggplot(TWBState, aes(y=TF17, x=TWB18)) +
  geom_smooth(method=lm, se=FALSE) +
  xlab("Taxable Wage Base 2018 by State") +
  ylab("Trust Fund 2017 by State") +
  geom_text(label = TWBState$State, size = 2) +  
  coord_cartesian(ylim = c(0, 5000))
p5 <- ggplot(TWBState, aes(y=TF16, x=TWB17)) +
  geom_smooth(method=lm, se=FALSE) +
  xlab("Taxable Wage Base 2017 by State") +
  ylab("Trust Fund 2016 by State") +
  geom_text(label = TWBState$State, size = 2) +
  coord_cartesian(ylim = c(0, 5000))
p6 <- ggplot(TWBState, aes(y=TF15, x=TWB16)) +
  geom_smooth(method=lm, se=FALSE) +
  xlab("Taxable Wage Base 2016 by State") +
  ylab("Trust Fund 2015 by State") +
  geom_text(label = TWBState$State, size = 2) +
  coord_cartesian(ylim = c(0, 5000))

multiplot(p1, p2, p3, p4, p5, p6, cols=3)
```

## Scatterplot with adjusted TF, controlling for GDP.
```{r}
p1 <- ggplot(TWBState, aes(y=TF20, x=TWB21)) +
  geom_smooth(method=lm, se=FALSE, color = "#332288") +
  xlab("Taxable Wage Base 2021 by State") +
  ylab("Trust Fund 2020 by State (in millions)") +
  geom_text(label = TWBState$State, size = 4.5) +
  coord_cartesian(ylim = c(0, 5250))

Adjp1 <- ggplot(TWBState, aes(y=AdjTF20, x=TWB21)) +
  geom_smooth(method=lm, se=FALSE, color = "#332288") +
  xlab("Taxable Wage Base 2021 by State") +
  ylab("Trust Fund 2020 by State (in millions)") +
  geom_text(label = TWBState$State, size = 4.5) +
  coord_cartesian(ylim = c(0, 0.0013))
Adjp5 <- ggplot(TWBState, aes(y=AdjTF16, x=TWB17)) +
  geom_smooth(method=lm, se=FALSE, color = "#332288") +
  xlab("Taxable Wage Base 2017 by State") +
  ylab("Trust Fund 2016 by State (in millions)") +
  geom_text(label = TWBState$State, size = 2) +
  coord_cartesian(ylim = c(0, 0.0013))

multiplot(Adjp1, Adjp5, cols=2)
```


## Dumbbell State changes 20 to 15.
```{r}
class(TWBState$REG)
TWBState$REG <- factor(TWBState$REG, levels=as.character(TWBState$REG))
library(ggalt)
TFdumb1520 <- ggplot(TWBState, aes(x=TF15, xend=TF20, y= reorder(State, -TF15))) + 
        geom_dumbbell(size_x = 3,
                      colour_x = "#AA4499",
                      size_xend = 3,
                      colour_xend = "#332288",
                      size=1, 
                      dot_guide = TRUE) + 
  labs(x=NULL, y=NULL, 
             title="Trust Fund by State Dumbbell Chart", 
             subtitle="Change from 2015 vs 2020 in millions of dollars") +
        theme_classic()
plot(TFdumb1520)

## This shows an interesting point: every state/territory either managed to improve
## how much was in their trust fund or stay put with one lone exception: OK.
## And yet, they one of the higher TF amounts in 2015. What gives?
```


### WBA Comparison Visualized
## Taxable Wage Base
```{r}
WBABasep20 <- ggplot(TWBState, aes(y=MWBA20, x=TWB20)) +
  xlab("Taxable Wage Base 2020 by State") +
  ylab("Maximum Weekly Benefit Amount 2020 by State") +
  geom_smooth(method=lm, se=FALSE) +
  geom_text(label = TWBState$State, size = 3) +
  xlim(NA, 50000)
WBABasep16 <- ggplot(TWBState, aes(y=MWBA16, x=TWB16)) +
  xlab("Taxable Wage Base 2016 by State") +
  ylab("Maximum Weekly Benefit Amount 2016 by State") +
  geom_smooth(method=lm, se=FALSE) +
  geom_text(label = TWBState$State, size = 3) +
  xlim(NA, 50000)

multiplot(WBABasep20, WBABasep16, cols=2)
```

## Trust Fund
```{r}
WBAFundp20 <- ggplot(TWBState, aes(y=MWBA20, x=TF20)) +
  xlab("Trust Fund 2020 by State") +
  ylab("Maximum Weekly Benefit Amount 2020 by State") +
  geom_text(label = TWBState$State, size = 3) +
  coord_cartesian(xlim = c(0, 5250)) 
WBAFundp16 <- ggplot(TWBState, aes(y=MWBA16, x=TF16)) +
  xlab("Trust Fund 2016 by State") +
  ylab("Maximum Weekly Benefit Amount 2016 by State") +
  geom_text(label = TWBState$State, size = 3) +
  coord_cartesian(xlim = c(0, 5250))

multiplot(WBAFundp20, WBAFundp16, cols=2)
```

### By political leaning.
## Bar plot for TF levels, Pres Dem vs Repub.
```{r}
TWBState$RPE20 <- as.factor(TWBState$RPE20)

TFbpol20 <- ggplot(TWBState, aes(y=TF20/Pop20, x=RPE20, fill = RPE20)) +
  geom_bar(stat = "identity") +
  scale_fill_manual (values = c("#332288", "#661100"), 
                     labels = c("Democratic", "Republican"),
                     name = c("TF by Presidential Party")) +
  xlab("Electoral College Presidential Vote") +
  ylab("Trust Fund 2020 Amount (in millions)") +
  coord_cartesian(ylim = c(0, 0.010))

TWBState$RPE16 <- as.factor(TWBState$RPE16)

TFbpol16 <- ggplot(TWBState, aes(y=TF16/Pop16, x=RPE16, fill = RPE16)) +
  geom_bar(stat = "identity") +
  scale_fill_manual (values = c("#332288", "#661100"), 
                     labels = c("Democratic", "Republican"),
                     name = c("TF by Presidential Party")) +
  xlab("Electoral College Presidential Vote") +
  ylab("Trust Fund 2016 Amount (in millions)") +
  coord_cartesian(ylim = c(0, 0.010))

multiplot(TFbpol20, TFbpol16, cols=2)
```

## Bar plot for TWB levels.

## Political Highlights 20
```{r}
TWBFundRP20 <- ggplot(TWBState, aes(y=TWB20, x=TF20, color= factor(RP20))) +
  geom_smooth(method=lm, se=FALSE) +
  scale_color_manual(values = c("gray40","red")) +
  xlab("Trust Fund 2020 by State (in millions)") +
  ylab("Taxable Wage Base 2020 by State") +
  geom_text(label = TWBState$State, size = 4) + 
  coord_cartesian(xlim = c(0, 5250))
TWBFundRP20
TWBFundDP20 <- ggplot(TWBState, aes(y=TWB20, x=TF20, color= factor(RP20))) +
  geom_smooth(method=lm, se=FALSE) +
  scale_color_manual(values = c("blue", "gray40")) +
  xlab("Trust Fund 2020 by State (in millions)") +
  ylab("Taxable Wage Base 2020 by State") +
  geom_text(label = TWBState$State, size = 4) + 
  coord_cartesian(xlim = c(0, 5250))
TWBFundDP20
```
## Political Highlights 16
```{r}
TWBFundRP16 <- ggplot(TWBState, aes(y=TWB16, x=TF16, color= factor(RP16))) +
  geom_smooth(method=lm, se=FALSE) +
  scale_color_manual(values = c("gray40","red")) +
  xlab("Trust Fund 2016 by State (in millions)") +
  ylab("Taxable Wage Base 2016 by State") +
  geom_text(label = TWBState$State, size = 4) + 
  coord_cartesian(xlim = c(0, 5250))
TWBFundRP16
TWBFundDP16 <- ggplot(TWBState, aes(y=TWB16, x=TF16, color= factor(RP16))) +
  geom_smooth(method=lm, se=FALSE) +
  scale_color_manual(values = c("blue", "gray40")) +
  xlab("Trust Fund 2016 by State (in millions)") +
  ylab("Taxable Wage Base 2016 by State") +
  geom_text(label = TWBState$State, size = 4) + 
  coord_cartesian(xlim = c(0, 5250))
TWBFundDP16
```

## Political Highlights Multiplot 20 v 16
```{r}
multiplot(TWBFundRP16,TWBFundRP20, cols=2)
multiplot(TWBFundDP16,TWBFundDP20, cols=2)
```

## MAYBE HIGHLIGHT THOSE THAT SWITCHED PARTIES? (Use scatterplot encircling
## from master webpage for that.)
```{r}
chgstate20 <- TWBState[which(TWBState$RP20 == "1" & TWBState$DP16 == "1" | 
                         TWBState$DP20 == "1" & TWBState$RP16== "1")]
summary(chgstate20)
## I think this doesn't work because it doesn't include TF in it. Error reads
## "error in FUN(X[i]], ...): object 'TF20' not found." And based on the example
## online that looks to be correct. So add & operator in there with wide TF
## parameters, since we're looking more at who changed political sides.

TWBFundRPCir20 <- ggplot(TWBState, aes(y=TWB20, x=TF20, color= factor(RP20))) +
  geom_smooth(method=lm, se=FALSE) +
  scale_color_manual(values = c("gray40","red")) +
  geom_encircle(aes(y=TWB20, x=TF20),
                data = chgstate20,
                color = "purple3",
                size=1.75,
                expand = 0.05) +
  xlab("Trust Fund 2020 by State (in millions)") +
  ylab("Taxable Wage Base 2020 by State") +
  geom_text(label = TWBState$State, size = 4) + 
  coord_cartesian(xlim = c(0, 5250))
TWBFundRPCir20
TWBFundDP20 <- ggplot(TWBState, aes(y=TWB20, x=TF20, color= factor(RP20))) +
  geom_smooth(method=lm, se=FALSE) +
  scale_color_manual(values = c("blue", "gray40")) +
  xlab("Trust Fund 2020 by State (in millions)") +
  ylab("Taxable Wage Base 2020 by State") +
  geom_text(label = TWBState$State, size = 4) + 
  coord_cartesian(xlim = c(0, 5250))
TWBFundDP20

TWBFundRP16 <- ggplot(TWBState, aes(y=TWB16, x=TF16, color= factor(RP16))) +
  geom_smooth(method=lm, se=FALSE) +
  scale_color_manual(values = c("gray40","red")) +
  xlab("Trust Fund 2016 by State (in millions)") +
  ylab("Taxable Wage Base 2016 by State") +
  geom_text(label = TWBState$State, size = 4) + 
  coord_cartesian(xlim = c(0, 5250))
TWBFundRP16
TWBFundDP16 <- ggplot(TWBState, aes(y=TWB16, x=TF16, color= factor(RP16))) +
  geom_smooth(method=lm, se=FALSE) +
  scale_color_manual(values = c("blue", "gray40")) +
  xlab("Trust Fund 2016 by State (in millions)") +
  ylab("Taxable Wage Base 2016 by State") +
  geom_text(label = TWBState$State, size = 4) + 
  coord_cartesian(xlim = c(0, 5250))
TWBFundDP16
```


### By geographical region.

## Regional Highlights 20
```{r}
WBAFundMW20 <- ggplot(TWBState, aes(y=MWBA20, x=TF20, color= factor(REG))) +
  scale_color_manual(values = c("gray40", "gray40", "red", "gray40")) +
  xlab("Trust Fund 2020 by State (in millions)") +
  ylab("Maximum Weekly Benefit Amount 2020 by State") +
  geom_text(label = TWBState$State, size = 4) + 
  coord_cartesian(xlim = c(0, 5250))
WBAFundNE20 <- ggplot(TWBState, aes(y=MWBA20, x=TF20, color= factor(REG))) +
  scale_color_manual(values = c("gray40", "gray40", "gray40", "red")) +
  xlab("Trust Fund 2020 by State (in millions)") +
  ylab("Maximum Weekly Benefit Amount 2020 by State") +
  geom_text(label = TWBState$State, size = 4) + 
  coord_cartesian(xlim = c(0, 5250))
WBAFundS20 <- ggplot(TWBState, aes(y=MWBA20, x=TF20, color= factor(REG))) +
  scale_color_manual(values = c("gray40","red", "gray40", "gray40")) +
  xlab("Trust Fund 2020 by State (in millions)") +
  ylab("Maximum Weekly Benefit Amount 2020 by State") +
  geom_text(label = TWBState$State, size = 4) + 
  coord_cartesian(xlim = c(0, 5250))
WBAFundW20 <- ggplot(TWBState, aes(y=MWBA20, x=TF20, color= factor(REG))) +
  scale_color_manual(values = c("red", "gray40", "gray40", "gray40")) +
  xlab("Trust Fund 2020 by State (in millions)") +
  ylab("Maximum Weekly Benefit Amount 2020 by State") +
  geom_text(label = TWBState$State, size = 4) + 
  coord_cartesian(xlim = c(0, 5250))
```

## Regional Highlights 15
```{r}
WBAFundMW15 <- ggplot(TWBState, aes(y=MWBA15, x=TF15, color=REG)) +
  scale_color_manual(values = c("gray40", "gray40", "red", "gray40")) +
  xlab("Trust Fund 2015 by State (in millions)") +
  ylab("Maximum Weekly Benefit Amount 2015 by State") +
  geom_text(label = TWBState$State, size = 4) +
  coord_cartesian(xlim = c(0, 5250))
WBAFundNE15 <- ggplot(TWBState, aes(y=MWBA15, x=TF15, color=REG)) +
  scale_color_manual(values = c("gray40", "gray40", "gray40", "red")) +
  xlab("Trust Fund 2015 by State (in millions)") +
  ylab("Maximum Weekly Benefit Amount 2015 by State") +
  geom_text(label = TWBState$State, size = 4) +
  coord_cartesian(xlim = c(0, 5250))
WBAFundS15 <- ggplot(TWBState, aes(y=MWBA15, x=TF15, color=REG)) +
  scale_color_manual(values = c("gray40","red", "gray40", "gray40")) +
  xlab("Trust Fund 2015 by State (in millions)") +
  ylab("Maximum Weekly Benefit Amount 2015 by State") +
  geom_text(label = TWBState$State, size = 4) +
  coord_cartesian(xlim = c(0, 5250))
WBAFundW15 <- ggplot(TWBState, aes(y=MWBA15, x=TF15, color=REG)) +
  scale_color_manual(values = c("red", "gray40", "gray40", "gray40")) +
  xlab("Trust Fund 2015 by State (in millions)") +
  ylab("Maximum Weekly Benefit Amount 2015 by State") +
  geom_text(label = TWBState$State, size = 4) +
  coord_cartesian(xlim = c(0, 5250))
```

## Regional Highlights Multiplot 20 v 15
```{r}
multiplot(WBAFundMW15,WBAFundMW20, cols=2)
multiplot(WBAFundNE15,WBAFundNE20, cols=2)
multiplot(WBAFundS15,WBAFundS20, cols=2)
multiplot(WBAFundW15,WBAFundW20, cols=2)
```


## Bar color filled.
```{r}
TFbf20 <- ggplot(TWBState, aes(y=TF20, x=REG, fill = REG)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("purple4", "forestgreen", "dodgerblue3", "turquoise3")) +
  xlab("Geographic Regions") +
  ylab("Trust Fund 2020 Amount") +
  coord_cartesian(ylim = c(0, 23000))
TFbf16 <- ggplot(TWBState, aes(y=TF16, x=REG, fill = REG)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("purple4",  "forestgreen", "dodgerblue3", "turquoise3")) +
  xlab("Geographic Regions") +
  ylab("Trust Fund 2016 Amount") +
  coord_cartesian(ylim = c(0, 23000))

multiplot(TFbf16, TFbf20, cols=2)
```

## Bar with stripes to show where different states hit.
```{r}
TFbs16 <- ggplot(TWBState, aes(y=TF16, x=REG, color = REG)) +
  geom_bar(stat = "identity") +
  scale_color_manual(values = c("purple4", "forestgreen", "dodgerblue3", "turquoise3")) +
  xlab("Geographic Regions") +
  ylab("Trust Fund 2016 Amount") +
  coord_cartesian(ylim = c(0, 23000))
TFbs20 <- ggplot(TWBState, aes(y=TF20, x=REG, color = REG)) +
  geom_bar(stat = "identity") +
  scale_color_manual(values = c("purple4", "forestgreen", "dodgerblue3", "turquoise3")) +
  xlab("Geographic Regions") +
  ylab("Trust Fund 2020 Amount") +
  coord_cartesian(ylim = c(0, 23000))

multiplot(TFbs16, TFbs20, cols=2)
```

## Joyplot/Ridgeplot

```{r}
TFjoy20<- ggplot(TWBState, aes(x = TF20, y = REG, fill = REG)) +
  geom_density_ridges() +
  theme_ridges() + 
  theme(legend.position = "none") +
  scale_fill_manual(values = c("#88CCEE", "44AA99", "117733", "332288"))
TFjoy16 <- ggplot(TWBState, aes(x = TF16, y = REG, fill = REG)) +
  geom_density_ridges() +
  theme_ridges() + 
  theme(legend.position = "none") +
  scale_fill_manual(values = c("#88CCEE", "44AA99", "117733", "332288"))

multiplot(TFjoy20, TFjoy16, cols = 2)
## LEFT OFF HERE.
```


## Box and Whiskers of regions.
```{r}
TFbox16 <- ggplot(TWBState, aes(y=TF16, x=REG)) +
  geom_boxplot() +
  xlab("Geographic Regions") +
  ylab("Trust Fund 2016 Amount") +
  coord_cartesian(ylim = c(0, 5000))
TFbox20 <- ggplot(TWBState, aes(y=TF20, x=REG)) +
  geom_boxplot() +
  xlab("Geographic Regions") +
  ylab("Trust Fund 2020 Amount") +
  coord_cartesian(ylim = c(0, 5000))

multiplot(TFbox16, TFbox20, cols=2)
```

## Timelapse/line graph of regions, TFYear.
```{r}

TFYear$W <- c(TFYear$AK+TFYear$AZ+TFYear$CA+TFYear$CO+TFYear$HI+TFYear$ID 
              +TFYear$MT+TFYear$NV+TFYear$NM+TFYear$OR+TFYear$UT+TFYear$WA
              +TFYear$WY/13)
TFYear$MW <- c(TFYear$IL+TFYear$IN+TFYear$IA+TFYear$KS+TFYear$MI+TFYear$MN
               +TFYear$MO+TFYear$NE+TFYear$ND+TFYear$OH+TFYear$SD+TFYear$WI/12)
TFYear$S <- c(TFYear$AL+TFYear$AR+TFYear$DC+TFYear$FL+TFYear$GA+TFYear$KY+TFYear$LA
              +TFYear$MS+TFYear$NC+TFYear$OK+TFYear$PR+TFYear$TX+TFYear$VA
              +TFYear$VI+TFYear$WV/17)
TFYear$NE <- c(TFYear$CT+TFYear$ME+TFYear$MA+TFYear$NH+TFYear$NJ+TFYear$NY
               +TFYear$PA+TFYear$RI+TFYear$VT/9)

TFtYR <- ggplot() +
  geom_line(data=TFYear, aes(y=NE, x=Year, color="NE"), size = 1.1) +
  geom_line(data=TFYear, aes(y=S, x=Year, color="S"), size = 1.1) +
  geom_line(data=TFYear, aes(y=W, x=Year, color="W"), size = 1.1) +
  geom_line(data=TFYear, aes(y=MW, x=Year, color="MW"), size = 1.1) +
  xlab("Year") +
  ylab("TF Amounts") +
  ggtitle("Trust Fund Amounts 2015-2020 by Geographic Region") +
  scale_color_manual(values = c("purple4", "forestgreen", "dodgerblue3", 
                                "turquoise3"))

```

## Timelapse/line graph of regions, TWBYear.
```{r}
TWBYear$W <- c(TWBYear$AK+TWBYear$AZ+TWBYear$CA+TWBYear$CO+TWBYear$HI+TWBYear$ID 
              +TWBYear$MT+TWBYear$NV+TWBYear$NM+TWBYear$OR+TWBYear$UT+TWBYear$WA
              +TWBYear$WY/13)
TWBYear$MW <- c(TWBYear$IL+TWBYear$IN+TWBYear$IA+TWBYear$KS+TWBYear$MI+TWBYear$MN
               +TWBYear$MO+TWBYear$NE+TWBYear$ND+TWBYear$OH+TWBYear$SD+TWBYear$WI/12)
TWBYear$S <- c(TWBYear$AL+TWBYear$AR+TWBYear$DC+TWBYear$FL+TWBYear$GA+TWBYear$KY+TWBYear$LA
              +TWBYear$MS+TWBYear$NC+TWBYear$OK+TWBYear$PR+TWBYear$TX+TWBYear$VA
              +TWBYear$VI+TWBYear$WV/17)
TWBYear$NE <- c(TWBYear$CT+TWBYear$ME+TWBYear$MA+TWBYear$NH+TWBYear$NJ+TWBYear$NY
               +TWBYear$PA+TWBYear$RI+TWBYear$VT/9)

TWBtYR <- ggplot() +
  geom_line(data=TWBYear, aes(y=NE, x=Year, color="NE"), size = 1.1) +
  geom_line(data=TWBYear, aes(y=S, x=Year, color="S"), size = 1.1) +
  geom_line(data=TWBYear, aes(y=W, x=Year, color="W"), size = 1.1) +
  geom_line(data=TWBYear, aes(y=MW, x=Year, color="MW"), size = 1.1) +
  xlab("Year") +
  ylab("TWB Amounts") +
  ggtitle("Taxable Wage Bases 2015-2020 by Geographic Region") +
  scale_color_manual(values = c("purple4", "forestgreen", "dodgerblue3", 
                                "turquoise3"))

multiplot(TFtYR, TWBtYR, cols=2)
```


### By population.
## Barplot TF.
```{r}
## DON'T RUN ALL PACKAGES BEFORE RUNNING THESE. JUST INTRO, VISUALIZATION PACKAGES
## AND MULTIPLOT FUNCTION.

TFbpop19 <- ggplot(TWBState, aes(Pop19cat, TF19, fill = Pop19cat)) +
  geom_bar(stat="identity") +
  coord_flip() +
  scale_fill_manual(values = c("purple4", "forestgreen", "dodgerblue3", 
                                "turquoise3", "deepskyblue2")) +
  xlab("Population Levels in 2019") +
  ylab("Trust Fund 2019 Amount")
TFbpop16 <- ggplot(TWBState, aes(Pop16cat, TF16, fill = Pop16cat)) +
  geom_bar(stat="identity") +
  coord_flip() +
  scale_fill_manual(values = c("purple4", "forestgreen", "dodgerblue3", 
                                "turquoise3", "deepskyblue2")) +
  xlab("Population Levels in 2016") +
  ylab("Trust Fund 2016 Amount")

multiplot(TFbpop19, TFbpop15, cols=2)
```

## Density plot TF.
```{r}
TFdenpop19 <- ggplot(TWBState, aes(TF19))
TFdenpop19p <- TFdenpop19 + geom_density(aes(fill=factor(Pop19cat)), alpha=0.7) + 
    labs(title="Density Plot", 
         subtitle="Trust Fund Amount Grouped by Population Levels",
         x="Trust Fund Amount (in thousands)",
         fill="Population Levels 2019")

## This is cool, but I'm honestly not sure exactly how to interpret this. Will
## need clarification. On the web page I pulled it off of, it talks about how
## this shows "how several data points are distributed."
## In Landers, the difference between a histogram and a density plot is "histogram
## is discrete, density is continuous." (pg 88)
## Discrete is "can only take on certain values" whereas continous is "can take on
## "any value in a range." All this said, I think density makes more sense, since
## trust funds can be any figure between $0 to hundreds of millions of dollars.

TFdenpop16 <- ggplot(TWBState, aes(TF16))
TFdenpop16p <- TFdenpop16 + geom_density(aes(fill=factor(Pop17cat)), alpha=0.7) + 
    labs(title="Density Plot", 
         subtitle="Trust Fund Amount Grouped by Population Levels",
         x="Trust Fund Amount (in thousands)",
         fill="Population Levels 2016")

multiplot (TFdenpop16p, TFdenpop19p, cols=2)
```
