### UI Trust Fund, Taxable Wage Base, and Maximum Weekly Benefit Amount 
### Comparison Analysis

## Three data sets: "TWBState", "TWBYear", and "TFYear." "State" is IV state. 
## (This is the more frequently used of the set.) "Year" is IV year.

## X (Independent Variables) - Taxable Wage Base (TWB), Trust Fund (TF), Maximum
## Weekly Benefit Amount (MWBA).
## Y (Dependent variables) - Political party affiliation (Republican 
## Governor(RG) v Democratic Governor (DG), Republican President (RP) v 
## Democratic President (DP), Population, Geographic Area, and 
## Gross Domestic Product (GDP).

## Hypothesis 1: States with higher trust fund amounts will have higher taxable 
## wage base.
## H2: States with lower MWBA will have lower TWB, higher TFs.
## H3: In states that see a change from Republican to Democratic administrations,
## there will be higher TWBs, lower TFs, higher MWBAs.

library(readxl)
TWBState <- read_excel("C:/Users/Bridgette/Desktop/UI Tax Project/TWBState.xlsx", 
    guess_max = min(2000, n_max = NULL))
library(readxl)
TWBYear <- read_excel("C:/Users/Bridgette/Desktop/UI Tax Project/TWBYear.xlsx", 
    guess_max = min(2000, n_max = NULL))
library(readxl)
TFYear <- read_excel("C:/Users/Bridgette/Desktop//UI Tax Project/TFYear.xlsx", 
    guess_max = min(2000, n_max = NULL))

### NEED TO TAKE ADJUSTED TF AND APPLY IT TO EVERYTHING BELOW HETEROSKEDASTICITY.

### Regression analysis TWB by trust fund amount (current year)
```{r}
TFC20 <- lm(TF19 ~ TWB19, data = TWBState)
TFC16 <- lm(TF15 ~ TWB15, data = TWBState)
summary(TFC15)

## Nothing significant here.
```

## States by trust fund amount (prior year)
```{r}
TFP20 <- lm(TF19 ~ TWB20, data = TWBState)
summary(TFP20)
TFP16 <- lm(TF15 ~ TWB16, data = TWBState)
summary(TFP16)

## Again, nothing significant.
```

### Regression analysis TWB by MWBA
```{r}
WBAT20 <- lm(TWB20 ~ MWBA19, data = TWBState)
summary(WBAT20)
WBAT16 <- lm(TWB16 ~ MWBA15, data = TWBState)
summary(WBAT16)

## And here's where we start finding significance. We're seeing a range from
## 0.003-0.007 statistical significance across years. The 0.007 was the highest
## in 2015, after that it had an even stronger relationship between the two factors
## ranging from 0.004-0.003 in the last three years (2019-2021). *NOTE: This was
## staggered to review the previous year's MWBA to the next year's TWB.
```

## And TF by MWBA
```{r}
WBATF20 <- lm(TF20 ~ MWBA19, data = TWBState)
summary(WBATF20)
WBATF16 <- lm(TF16 ~ MWBA15, data = TWBState)
summary(WBATF16)

## Now, this is an interesting turn around. Where the taxable wage base had a
## statistically significant relationship with MWBA, the trust fund does not at
## all. 
```

### OLS Calibrations.
## Improved regression (heteroskedasticity) - TWB
ImprTWB21R <- lm(TWB21 ~ RG21 + RP20, data = TWBPolState, 
                  na.action = na.exclude)
summary(ImprTWB21R)
bptest(ImprTWB21R, studentize = FALSE)
## Not statistically significant, so no heteroskedasticity.

## Improved regression (heteroskedasticity) - TF
ImprTF20R <- lm(TF20 ~ RG20 + RP20, data = TWBPolState, 
                  na.action = na.exclude)
summary(ImprTF20R)
bptest(ImprTF20R, studentize = FALSE)

## This is statistically significant, so we do have heteroskedasticity.
```{r}
ImprTF19R <- lm(TF19 ~ RG19, data = TWBState, 
                  na.action = na.exclude)
summary(ImprTF19R)
bptest(ImprTF19R, studentize = FALSE)
ImprTF18R <- lm(TF18 ~ RG18, data = TWBState, 
                  na.action = na.exclude)
summary(ImprTF18R)
bptest(ImprTF18R, studentize = FALSE)
ImprTF17R <- lm(TF17 ~ RG17, data = TWBState, 
                  na.action = na.exclude)
summary(ImprTF17R)
bptest(ImprTF17R, studentize = FALSE)
ImprTF16R <- lm(TF16 ~ RG16 + RP16, data = TWBState, 
                  na.action = na.exclude)
summary(ImprTF16R)
bptest(ImprTF16R, studentize = FALSE)
ImprTF15R <- lm(TF15 ~ RG15, data = TWBState, 
                  na.action = na.exclude)
summary(ImprTF15R)
bptest(ImprTF15R, studentize = FALSE)
```

## Every year is statistically significant, some pretty dramatically so. We'll 
## work on getting it fixed.

### Fixing heteroskedasticity for TF.
```{r}
## Hetero or homo-skedastic?
varTF20 <- summary(ImprTF20R)
SERTF20 <- varTF20$sigma
varTWB20 <- (nrow(TWBState)-1) * var(TWBState$TWB20)
SETF20 <- sqrt(SERTF20)
round(varTF20$coefficients[2,2], 4) == round(SETF20)
## Hetero. 

AdjTF15 <- TWBState$TF15/TWBState$Pop15
AdjTF16 <- TWBState$TF16/TWBState$Pop16
AdjTF17 <- TWBState$TF17/TWBState$Pop17
AdjTF18 <- TWBState$TF18/TWBState$Pop18
AdjTF19 <- TWBState$TF19/TWBState$Pop19
AdjTF20 <- TWBState$TF20/TWBState$Pop20

AdjTFTWBGDP20 <- lm(AdjTF20 ~ TWB20 + GDP20, data = TWBState)
summary(AdjTFTWBGDP20)
AdjTFTWB20 <- lm(AdjTF20 ~ TWB20, data = TWBState)
summary(AdjTFTWB20)
AdjTFTWB16 <- lm(AdjTF16 ~ TWB16 + GDP16, data = TWBState)
summary(AdjTFTWB16)

TWBState$logTF20 <- log(TWBState$TF20)
AdjTF20RPP <- lm(AdjTF20 ~ RG20 + RPP20 + GDP20, data = TWBState)
summary(AdjTF20RPP)
bptest(AdjTF20RPP, studentize = FALSE)
AdjTF20RPE <- lm(AdjTF20 ~ RG20 + RPE20 + GDP20, data = TWBState)
summary(AdjTF20RPE)
bptest(AdjTF20RPE, studentize = FALSE)
AdjTF16RPP <- lm(AdjTF15 ~ RG16 + RPP16 + GDP16, data = TWBState)
summary(AdjTF16RPP)
bptest(AdjTF16RPP, studentize = FALSE)
AdjTF16RPE <- lm(AdjTF16 ~ RG16 + RPE16 + GDP16, data = TWBState)
summary(AdjTF16RPE)
bptest(AdjTF16RPE, studentize = FALSE)

```


## Checking for multicollinearity in variables - TWB
vif(TWB21RMult)
## No multicollinearity problem, as they are both rather close to 1 at 1.02.
vif(TF20RMult)
## No multicollinearity problem, as they are both at 1.01.


### Multiple regression TWB/TF (controlling for Governor, Presidential Party 
## preference)

## 2020 Presidential Run
```{r}
TWB20RPP <- lm(TWB20 ~ RG20 + RPP20 + GDP20, data = TWBState)
summary(TWB20RPP)
TWB20DPP <- lm(TWB20 ~ DG20 + DPP20 + GDP20, data = TWBState)
summary(TWB20DPP)
TWB20RPE <- lm(TWB20 ~ RG20 + RPE20 + GDP20, data = TWBState)
summary(TWB20RPE)
TWB20DPE <- lm(TWB20 ~ DG20 + DPE20 + GDP20, data = TWBState)
summary(TWB20DPE)


TF20RPP <- lm(AdjTF20 ~ RG20 + RPP20 + GDP20, data = TWBState)
summary(TF20RMult)
TF20DPP <- lm(AdjTF20 ~ DG20 + DPP20 + GDP20, data = TWBState)
summary(TF20DMult)
TF20RPE <- lm(AdjTF20 ~ RG20 + RPE20 + GDP20, data = TWBState)
summary(TF20RMult)
TF20DPE <- lm(AdjTF20 ~ DG20 + DPE20 + GDP20, data = TWBState)
summary(TF20DMult)

## No statistical significance here. The taxable wage base seems to have less of
## a relationship than trust fund, but either way it's not enough
## to show any sort of relationship with political leaning of a state and
## taxable wage base/trust fund in 2020.
```

## 2016 Presidential Run (TWB/TF)
```{r}
TWB16RPE <- lm(TWB16 ~ RG16 + RPE16 + GDP16, data = TWBState)
summary(TWB16RPE)
TWB16DPE <- lm(TWB16 ~ DG16 + DPE16 + GDP16, data = TWBState)
summary(TWB16DPE)
TWB16RPP <- lm(TWB16 ~ RG16 + RPP16 + GDP16, data = TWBState)
summary(TWB16RPP)
TWB16DPP <- lm(TWB16 ~ DG16 + DPP16 + GDP16, data = TWBState)
summary(TWB16DPP)

TF16RPE <- lm(TF16 ~ RG16 + RPE16 + GDP16, data = TWBState)
summary(TF16RPE)
TF16DPE <- lm(TF16 ~ DG16 + DPE16 + GDP16, data = TWBState)
summary(TF16DPE)
TF16RPP <- lm(TF16 ~ RG16 + RPP16 + GDP16, data = TWBState)
summary(TF16RPP)
TF16DPP <- lm(TF16 ~ DG16 + DPP16 + GDP16, data = TWBState)
summary(TF16DPP)

## It seems like 2016 was close enough to show some relationship between taxable
## wage base/trust fund and partisan political leaning. The way it breaks out is 
## intriguing. For the taxable wage base, the presidential race on both sides
## of the aisle showed significance at the 0.1-0.05 level. For the trust fund, the
## gubernatorial race was where the relationship showed at the 0.01 level, so
## slightly stronger. 
```


### States by geographic location regression analysis

## 2021
```{r}
S21 <- lm(TWB21 ~ S, data = TWBState) 
summary(S21)
NE21 <- lm(TWB21 ~ NE, data = TWBState) 
summary(NE21)
W21 <- lm(TWB21 ~ W, data = TWBState) 
summary(W21)
MW21 <- lm(TWB21 ~ MW, data = TWBState) 
summary(MW21)
```

## 2020
```{r}
S20 <- lm(TWB20 ~ S, data = TWBState) 
summary(S20)
NE20 <- lm(TWB20 ~ NE, data = TWBState) 
summary(NE20)
W20 <- lm(TWB20 ~ W, data = TWBState) 
summary(W20)
MW20 <- lm(TWB20 ~ MW, data = TWBState) 
summary(MW20)
```

## 2019
```{r}
S19 <- lm(TWB19 ~ S, data = TWBState) 
summary(S19)
NE19 <- lm(TWB19 ~ NE, data = TWBState) 
summary(NE19)
W19 <- lm(TWB19 ~ W, data = TWBState) 
summary(W19)
MW19 <- lm(TWB19 ~ MW, data = TWBState) 
summary(MW19)
```

## 2018
```{r}
S18 <- lm(TWB18 ~ S, data = TWBState) 
summary(S18)
NE18 <- lm(TWB18 ~ NE, data = TWBState) 
summary(NE18)
W18 <- lm(TWB18 ~ W, data = TWBState) 
summary(W18)
MW18 <- lm(TWB18 ~ MW, data = TWBState) 
summary(MW18)
```

## 2017
```{r}
S17 <- lm(TWB17 ~ S, data = TWBState) 
summary(S17)
NE17 <- lm(TWB17 ~ NE, data = TWBState) 
summary(NE17)
W17 <- lm(TWB17 ~ W, data = TWBState) 
summary(W17)
MW17 <- lm(TWB17 ~ MW, data = TWBState) 
summary(MW17)
```

## 2016
```{r}
S16 <- lm(TWB16 ~ S, data = TWBState) 
summary(S16)
NE16 <- lm(TWB16 ~ NE, data = TWBState) 
summary(NE16)
W16 <- lm(TWB16 ~ W, data = TWBState) 
summary(W16)
MW16 <- lm(TWB16 ~ MW, data = TWBState) 
summary(MW16)
```

## 2015  
```{r}
S15 <- lm(TWB15 ~ S, data = TWBState) 
summary(S15)
NE15 <- lm(TWB15 ~ NE, data = TWBState) 
summary(NE15)
W15 <- lm(TWB15 ~ W, data = TWBState) 
summary(W15)
MW15 <- lm(TWB15 ~ MW, data = TWBState) 
summary(MW15)
```

## MW Only Regression
```{r}
MWTF20 <- lm(TF20 ~ TWB21+TWB20+TWB19+TWB18+TWB17+TWB16, data = MWonly)
summary (MWTF20)
MWTF19 <- lm(TF19 ~ TWB21+TWB20+TWB19+TWB18+TWB17+TWB16, data = MWonly)
summary (MWTF19)
MWTF18 <- lm(TF18 ~ TWB21+TWB20+TWB19+TWB18+TWB17+TWB16, data = MWonly)
summary (MWTF18)
MWTF17 <- lm(TF17 ~ TWB21+TWB20+TWB19+TWB18+TWB17+TWB16, data = MWonly)
summary (MWTF17)
MWTF16 <- lm(TF16 ~ TWB21+TWB20+TWB19+TWB18+TWB17+TWB16, data = MWonly)
summary (MWTF16)
MWTF15 <- lm(TF15 ~ TWB21+TWB20+TWB19+TWB18+TWB17+TWB16, data = MWonly)
summary (MWTF15)
```


### Mult regression analysis TWB by region
## (RTWB == Regional TWB, RTF == Regional TF) MW is the control group. 

```{r}
RTWB21 <- lm(TWB21 ~ S + NE + W + MW, data = TWBState)
summary(RTWB21)
RTWB20 <- lm(TWB20 ~ S + NE + W + MW + GDP20, data = TWBState)
summary(RTWB20)
RTWB19 <- lm(TWB19 ~ S + NE + W + MW + GDP19, data = TWBState)
summary(RTWB19)
RTWB18 <- lm(TWB18 ~ S + NE + W + MW + GDP18, data = TWBState)
summary(RTWB18)
RTWB17 <- lm(TWB17 ~ S + NE + W + MW + GDP17, data = TWBState)
summary(RTWB17)
RTWB16 <- lm(TWB16 ~ S + NE + W + MW GDP16, data = TWBState)
summary(RTWB16)
RTWB15 <- lm(TWB15 ~ S + NE + W + MW GDP15, data = TWBState)
summary(RTWB15)
```

### Mult regression analysis TF by region
```{r}
RTF20 <- lm(AdjTF20 ~ S + NE + W + MW + GDP20, data = TWBState)
summary(RTF20)
RTF19 <- lm(AdjTF19 ~ S + NE + W + MW + GDP19, data = TWBState)
summary(RTF19)
RTF18 <- lm(AdjTF18 ~ S + NE + W + MW + GDP18, data = TWBState)
summary(RTF18)
RTF17 <- lm(AdjTF17 ~ S + NE + W + MW + GDP17, data = TWBState)
summary(RTF17)
RTF16 <- lm(AdjTF16 ~ S + NE + W + MW + GDP16, data = TWBState)
summary(RTF16)
RTF15 <- lm(AdjTF15 ~ S + NE + W + MW + GDP15, data = TWBState)
summary(RTF15)
```


## Setting population categories

```{r}
TWBState %>% mutate(Pop19cat = cut(Pop19, breaks = c(-Inf, 1360000, 3200000, 
                                                        6200000, 12700000, Inf), 
                                      labels = c ("<1360000", "1360001-3200000",
                                                      "3200001-6200000", 
                                                      "6200001-12700000",
                                                      ">12700001")))
TWBState$Pop19cat <- cut(TWBState$Pop19, c(-Inf, 1360000, 3200000, 6200000, 
                                                 12700000, Inf),
                            labels = c ("<1360000", "1360001-3200000", 
                                        "3200001-6200000", "6200001-12700000",
                                        ">12700001"))

TWBState %>% mutate(Pop18cat = cut(Pop18, breaks = c(-Inf, 1360000, 3200000, 
                                                        6200000, 12700000, Inf), 
                                      labels = c ("<1360000", "1360001-3200000",
                                                      "3200001-6200000", 
                                                      "6200001-12700000",
                                                      ">12700001")))
TWBState$Pop18cat <- cut(TWBState$Pop18, c(-Inf, 1360000, 3200000, 6200000, 
                                                 12700000, Inf),
                            labels = c ("<1360000", "1360001-3200000", 
                                        "3200001-6200000", "6200001-12700000",
                                        ">12700001"))

TWBState %>% mutate(Pop17cat = cut(Pop17, breaks = c(-Inf, 1360000, 3200000, 
                                                        6200000, 12700000, Inf), 
                                      labels = c ("<1360000", "1360001-3200000",
                                                      "3200001-6200000", 
                                                      "6200001-12700000",
                                                      ">12700001")))
TWBState$Pop17cat <- cut(TWBState$Pop17, c(-Inf, 1360000, 3200000, 6200000, 
                                                 12700000, Inf),
                            labels = c ("<1360000", "1360001-3200000", 
                                        "3200001-6200000", "6200001-12700000",
                                        ">12700001"))

TWBState %>% mutate(Pop16cat = cut(Pop16, breaks = c(-Inf, 1360000, 3200000, 
                                                        6200000, 12700000, Inf), 
                                      labels = c ("<1360000", "1360001-3200000",
                                                      "3200001-6200000", 
                                                      "6200001-12700000",
                                                      ">12700001")))
TWBState$Pop16cat <- cut(TWBState$Pop16, c(-Inf, 1360000, 3200000, 6200000, 
                                                 12700000, Inf),
                            labels = c ("<1360000", "1360001-3200000", 
                                        "3200001-6200000", "6200001-12700000",
                                        ">12700001"))

TWBState %>% mutate(Pop15cat = cut(Pop15, breaks = c(-Inf, 1360000, 3200000, 
                                                        6200000, 12700000, Inf), 
                                      labels = c ("<1360000", "1360001-3200000",
                                                      "3200001-6200000", 
                                                      "6200001-12700000",
                                                      ">12700001")))
TWBState$Pop15cat <- cut(TWBState$Pop15, c(-Inf, 1360000, 3200000, 6200000, 
                                                 12700000, Inf),
                            labels = c ("<1360000", "1360001-3200000", 
                                        "3200001-6200000", "6200001-12700000",
                                        ">12700001"))

## Changes in category: 15 (IL) down to 6200001-12700000 in 2019, 42 (SC) down to 1360001-3200000  
##  in 2018 + 2019, and 46 (UT) up to 3200001-6200000 in 2019.
```

### Regression analysis TWB by population
## (PTWB == Population TWB, PTF == Population TF)

## LEFT OFF HERE.
## NEED TO DECIDE IF METRICS ON TF ARE GOING TO BE SET BACK A YEAR OR LEFT IN THE
## SAME YEAR.
```{r}
PTWB19 <- lm(TWB19 ~ Pop19cat, data = TWBState)
summary(PTWB19)
PTWB18 <- lm(TWB18 ~ Pop18cat, data = TWBState)
summary(PTWB18)
PTWB17 <- lm(TWB17 ~ Pop17cat, data = TWBState)
summary(PTWB17)
PTWB16 <- lm(TWB16 ~ Pop16cat, data = TWBState)
summary(PTWB16)
PTWB15 <- lm(TWB15 ~ Pop15cat, data = TWBState)
summary(PTWB15)
```

### Regression analysis TF by population
## (PTWB == Population TWB, PTF == Population TF)

```{r}
PTF19 <- lm(TF19 ~ Pop19cat, data = TWBState)
summary(PTF19)
PTF18 <- lm(TF18 ~ Pop18cat, data = TWBState)
summary(PTF18)
PTF17 <- lm(TF17 ~ Pop17cat, data = TWBState)
summary(PTF17)
PTF16 <- lm(TF16 ~ Pop16cat, data = TWBState)
summary(PTF16)
PTF15 <- lm(TF15 ~ Pop15cat, data = TWBState)
summary(PTF15)
```
